---
title: "REBL Scale"
author: "Dr. Trisha Shrum, Chris Donovan\n"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
    github_document:
        toc: true
        toc_depth: 1
        html_preview: true
    html_document:
        toc: true
        toc_depth: 1
        number_sections: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  results = 'hide',
  comment = "#>"
)
pacman::p_load(
  dplyr,
  eRm
)
```

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/tshrum/rebl/graph/badge.svg)](https://app.codecov.io/gh/tshrum/rebl)
<!-- badges: end -->

## Introduction

This is the repository for the Repeated Environmental Behavior Latent (REBL) Scale project. It contains all the code to build the REBL scale from raw data through visualizations. 

## REBL Package

### Installation

To install the `rebl` package:

```{r eval = FALSE}
# install.packages('remotes')
remotes::install_github('tshrum/rebl')
```

### Using the Package

#### Recoding Survey

```{r output = FALSE}
library(rebl)

# Example data frame
str(raw_example)

# Identify REBL items with regex. 
# Here we take everything that does not start with 'res'
(rebl_items <- id_rebl_items(raw_example, '^(?!res).*', perl = TRUE))

# Recode REBL items from Yes/No to 1/0
df <- recode_rebl(raw_example, rebl_items)

# To reverse code reversed REBL items (where 0 is the PEB), first identify them.
# Just using all food items as an example
(reversed_items <- id_reversed_rebl_items(rebl_items, '^food'))

# Now recode the reversed items in the df
df <- reverse_code_rebl_items(df, reversed_items)
```

#### Getting REBL Scores


```{r output = FALSE}
# Run Rasch Model
model <- get_rasch_model(df, 'respondent_id', rebl_items)

# Throws warning if some items are not found in df
model <- get_rasch_model(df, 'respondent_id', c(rebl_items, 'ffff', 'zzzz'))

# Get a df of REBL scores and person fit statistics
rebl_scores <- get_rebl_scores(model)

# Only REBL scores, no fits
rebl_only <- get_rebl_scores(model, include_fits = FALSE)
```


### File Structure

The project is halfway through transitioning into a package (2025-09-03). The package has the usual structure:

-   `R/`: Functions
-   `data/`: Built-in datasets. Used in examples and testing.
-   `data-raw/`: Scripts to create built-in datasets.
-   `man/`: Documentation
-   `tests/`: Test suite using `testthat`
-   `DESCRIPTION`: Package information, license, author
-   `NAMESPACE`: Exports and imports

In the meantime, functions will be duplicated across `3_functions/` and `R/` until things are settled, at which point I hope to clear this up and create a more focused, functional, and portable workflow.

## REBL Project

### Clone Repository

### Dependencies

The project is set up with `renv`. To restore the packages used in the project, use:

```
# install.packages('renv')
renv::restore()
```

This will install packages and versions as described in the `renv.lock` file.

### Navigating the Project

After opening `reb_scale.Rproj`, start with `table_of_contents.R`. This will list all the relevant scripts in the order they should be run. Run the `housekeeping.R` script, which will load helper functions that are used throughout the project. Additional required packages are then included in the top of each script. Using `ctrl/cmd + left click` on the text of a file path in the table of contents will open that script in a new tab. 

All the objects and packages required for each script are loaded at the top of the page, and all important outputs are saved at the end of each script. So, you can run the entire project from the table of contents, but you can also just skip to any script and run it from there.


### Project File Structure

-   `1_raw/` is for raw, untouched, datasets. Metadata is embedded into these files using # as a comment symbol.
-   `2_clean/` is for cleaned (wrangled, recoded, imputed, etc.) data.
-   `3_functions/` is where custom functions are stored. The housekeeping script will load these. 
-   `4_scripts/` is for all R scripts.
-   `5_objects/` is for intermediate .rds objects.
-   `6_outputs/` is where tabular outputs are kept.
-   `7_plots/` is for figures, diagrams, pngs, pdfs, etc.

