---
title: "REBL"
author: "Chris Donovan, Dr. Trisha Shrum\n"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
    github_document:
        toc: true
        toc_depth: 1
        html_preview: true
    html_document:
        toc: true
        toc_depth: 1
        number_sections: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  results = 'hide',
  comment = "#>"
)
pacman::p_load(
  dplyr,
  eRm
)
```

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/ChrisDonovan307/rebl/graph/badge.svg)](https://app.codecov.io/gh/ChrisDonovan307/rebl)
<!-- badges: end -->

## Introduction

This is the repository for the Repeated Environmental Behavior Latent (REBL) Scale project. It contains all the code to build the REBL scale from raw data through visualizations. 

## REBL Package

### Installation

To install the `rebl` package:

```{r eval = FALSE}
if (!require('remotes')) install.packages('remotes')
remotes::install_github('tshrum/rebl')
```

### Usage

See vignette for an example of how to use the package.

## REBL Calculator

There is also a [REBL Score Calculator](https://cdonov12.w3.uvm.edu/rebl_calculator/) that will take a dataset and produce all the results you might need for you. Note that it currently has a limited range of applications, but will be updated with more features and broader use cases shortly.
